A Comparative Quality Metric for Untargeted Fuzzing with Logic State Coverage

### 2024-08-18 paper/main.tex
checkpt
Adding the mention about the preliminary evaluation

@@

\subsection{Experiment Setup}

\subsection{Measurement Overheads}

\subsection{General-purpose Fuzzing}

\subsection{Hypervisor Fuzzing}

% same cov: what can we learn more from logic state cov?

\subsection{Grammar Fuzzing}

% init corpus cov: what can we learn more from logic state cov?

>>>>

\begin{figure*}[t]
  \centering
  \includegraphics[width=0.8\textwidth]{images/aflpp-xmllint-epfl.pdf}
  \caption{24-hour fuzzing campaign of XMLLint on AFL++. (Ins: instantaneous,
    Avg: average)}
  \label{f:aflpp-xmllint-epfl}
\end{figure*}

@@

\subsection{Preliminary Result}

\autoref{f:aflpp-xmllint-epfl} shows the preliminary evaluation result
using XMLLint and AFL++. The evaluation was done on a Intel Core i7-8665U CPU
machine with 16 GB of memory. The logic state coverage (left) shows the covered
distinctive logic states over time. The new coverage per second (middle) shows
the number of newly discovered logic states per time, while the new coverage per
execution (right) shows the percentage of executions that discovered new logic
states per execution. \textsc{Avg} indicates the average new coverage per second
or per execution, and \textsc{Ins} indicates the instantaneous new coverage
during the last 10-second measurement frame.

The logic state coverage increases steadily over time, but it gradually slows
down toward the 24-hour mark. This trend is also reflected in the new coverage
plot, where the average new coverage slowly decreases to a steady point toward
the end of the fuzzing campaign.

The sporadic peaks in the instantaneous new coverage plot (\textsc{Ins}) are
mainly due to the favorable in-flight seeds at the moment, which allowed AFL++
to execute XMLLint quicker. This results in more peaks in the "per second" plot
than in the "per execution" plot, where the discovered new logic states were
bigger than the average but the percentage of new logic states per execution
remained low.

%\subsection{Experiment Plan}
%
%\subsection{Measurement Overheads}
%\subsection{General-purpose Fuzzing}
%\subsection{Hypervisor Fuzzing}
  % same cov: what can we learn more from logic state cov?
%\subsection{Grammar Fuzzing}
  % init corpus cov: what can we learn more from logic state cov?
